\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage{enumitem}
\usepackage{seqsplit}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}
\emergencystretch=4em

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Zeta}{\zeta}
\newcommand{\Lean}[1]{\texttt{\seqsplit{#1}}}
\newcommand{\RH}{\texttt{RiemannHypothesis}}
\newcommand{\repo}{\url{https://github.com/thiagomassensini/dyadic_geometry_zeta_fuction}}

\title{A Formal C2 Route to Off-Critical Nonvanishing for the Riemann Zeta Function}
\author{Thiago F. M. Massensini Silva}
\date{Peer-review draft, v1.1.0}

\begin{document}

\maketitle

\begin{abstract}
We introduce a dyadic carry framework C2 and define the genuine analytic
numerator \(F(s)=D_\infty(s)-B_\infty(s)\).  In the half-plane of absolute
convergence the C2 bracket bijection gives an exact lateral cancellation, and
the remaining central tower yields the identity \(F(s)=c_0(s)\zeta(s)\), with
an explicit nonzero normalizing factor \(c_0\).  The C2 geometry has an internal
barrier at \(\operatorname{Re}(s)=1/2\): the branch norm depends only on
\(\sigma=\operatorname{Re}(s)\), while the transversal tilt detects displacement
from the critical line.  The proof route combines near-critical-zero rigidity,
middle-region resolvent non-cancellation, cutoff/residual control, and a
regional gluing argument.  The accompanying Lean development exposes the
audited route through \texttt{LeanC2.PeerReview}; its terminal public theorem is
the certified implication displayed in Theorem~\ref{thm:terminal-implication},
from a terminal C2
certificate to mathlib's official \RH{} statement.  This draft gives the human
mathematical route and records the exact Lean correspondence for external
audit.
\end{abstract}

\section{Introduction}

The Riemann hypothesis may be formulated as a nonvanishing statement for
\(\Zeta(s)\) away from the critical line inside the critical strip.  The C2
development studied here approaches that problem through a genuine dyadic
numerator
\[
  F(s):=D_\infty(s)-B_\infty(s),
\]
a formal identity relating \(F\) to \(\Zeta\), and a certificate-driven proof of
nonvanishing for \(F\) on the off-critical strip.

The route has the following form:
\[
\begin{gathered}
\text{C2 bracket geometry}
  \longrightarrow \text{genuine numerator }F
  \longrightarrow F=c_0\zeta \\
  \longrightarrow \text{near/bulk/edge certificates}
  \longrightarrow \text{off-critical regional cover}
  \longrightarrow F(s)\ne 0 \text{ off-axis} \\
  \longrightarrow \text{C2/zeta transfer}
  \longrightarrow \text{off-critical nonvanishing of } \Zeta
  \longrightarrow \RH .
\end{gathered}
\]

The main design choice is to separate the analytic obligations from the
transport and assembly lemmas.  In the Lean development, the terminal theorem is
not stated as an informal collection of hidden hypotheses.  Instead, it consumes
an inhabitant of the certificate type:
\[
  \Lean{C2.PeerReview.RiemannHypothesisTerminalCertificate}.
\]
The theorem
\[
  \Lean{C2.PeerReview.RiemannHypothesis\_of\_terminalCertificate}
\]
then returns mathlib's \RH{} proposition.

\subsection{Main statements}

\begin{theorem}[Lean-certified terminal implication]
\label{thm:terminal-implication}
In the review-facing Lean facade, the following theorem is checked:
\begin{quote}\small
\begin{verbatim}
C2.PeerReview.RiemannHypothesis_of_terminalCertificate :
  C2.PeerReview.RiemannHypothesisTerminalCertificate ->
  RiemannHypothesis
\end{verbatim}
\end{quote}
\end{theorem}

For audit clarity, the current review facade does not expose a closed
zero-argument constant named \Lean{C2.PeerReview.terminalCertificate}.  The
formal claim recorded in this draft is therefore the certified implication from
the terminal certificate interface, together with the public inventory of the
fields and obligations needed to inhabit that interface.  The same facade also
exposes the canonical assembly layer
\begin{quote}\small
\begin{verbatim}
C2.PeerReview.TerminalCertificate_of_continuedModelMiddleLocal
C2.PeerReview.RiemannHypothesis_of_continuedModelMiddleLocal
\end{verbatim}
\end{quote}
which builds the terminal package and derives \RH{} from the canonical
near-axis certificate for the continued C2 model together with the canonical
middle-local witness.  In addition, the facade exposes sharper endpoints where
the middle-local witness is replaced by pointwise horizontal-budget and
residual-dominance hypotheses:
\begin{quote}\small
\Lean{C2.PeerReview.TerminalCertificate\_of\_continuedModelCanonicalClosedScaledMiddleResidualPointwiseBounds}\\
\Lean{C2.PeerReview.RiemannHypothesis\_of\_continuedModelCanonicalClosedScaledMiddlePointwiseBounds}\\
\Lean{C2.PeerReview.RiemannHypothesis\_of\_continuedModelCanonicalClosedScaledMiddleResidualPointwiseBounds}\\
\Lean{C2.PeerReview.RiemannHypothesis\_of\_continuedModelCanonicalClosedScaledMiddleResidualAnalyticBounds}
\end{quote}
The continuation-based constructor remains available as an alternate audit
interface, but the current terminal assembly no longer needs it for the
near-axis package.  Thus the terminal certificate is an audit boundary for the
current route, not a hidden or informal premise.

\begin{theorem}[C2 mathematical route, informal]
The intended mathematical route is to prove that the genuine C2 numerator
\(F=D_\infty-B_\infty\) is nonvanishing on the off-critical strip.  Since
\(F=c_0\Zeta\) and \(c_0\) is nonzero there, this transfers to off-critical
nonvanishing of \(\Zeta\), and hence to mathlib's \RH{} statement.
\end{theorem}

\subsection{Contributions}

This paper records the following review-facing contributions.

\begin{enumerate}[label=(\roman*)]
  \item A dyadic bracket decomposition for odd integers and a formal lateral
    cancellation theorem for \(D_\infty-B_\infty\).
  \item A genuine-first identity \(F=c_0\zeta\), with \(F=D_\infty-B_\infty\)
    and explicit \(c_0\).
  \item A formal C2/zeta transfer layer from C2 operator nonvanishing to
    off-critical nonvanishing of \(\Zeta\), and hence to mathlib's \RH{}.
  \item A regional-cover abstraction for the off-critical strip.
  \item A continuation package for the genuine C2 operator and its
    near-critical-zero certificate.
  \item A middle-region nonvanishing interface based on resolvent
    non-cancellation: a dominant four-level block is compared against explicit
    residual budgets.
  \item A terminal certificate interface and checked Lean endpoint wrapper that
    assemble the route once the certificate fields are supplied.
\end{enumerate}

\subsection{Audit boundary}

The formalization deliberately distinguishes three kinds of statements.

\begin{enumerate}[label=(\arabic*)]
  \item Conceptual proof architecture: identity, cover, near-critical-zero
    nonvanishing, middle-region non-cancellation, edge handling, and transfer.
  \item Certificate data: bound packages, residual budgets, local witnesses,
    oscillatory witnesses, and cover data.
  \item Lean wrappers and packaging lemmas: aliases and theorem wrappers in the
    review-facing facade \Lean{LeanC2.PeerReview}.
\end{enumerate}

The central endpoint theorem is therefore best read as a checked contract:
given the terminal C2 certificate, Lean derives the official \RH{} proposition.
The certificate inventory is public and is documented in
\Lean{docs/BOUNDS\_CERTIFICATES\_WITNESSES.md}.

\section{The C2 dyadic decomposition}

The elementary C2 address system is defined by the two-adic valuation
\[
  v_2(n)=\max\{k:2^k\mid n\}.
\]
For an odd integer \(n\ge 3\), its effective C2 depth is
\[
  k_{\mathrm{eff}}(n)=
  \max\bigl(v_2(n-1),v_2(n+1)\bigr).
\]
A C2 center has the form
\[
  c=2^k m,\qquad k\ge 2,\qquad m\ \text{odd},
\]
and its two odd legs are \(c-1\) and \(c+1\).

\begin{theorem}[C2 bracket bijection]
Every odd integer \(n\ge 3\) appears as exactly one leg of exactly one C2
bracket.  More precisely, if \(c=2^k m\) with \(k\ge 2\) and \(m\) odd, then
\[
  k_{\mathrm{eff}}(c-1)=k_{\mathrm{eff}}(c+1)=k.
\]
Conversely, every odd \(n\ge 3\) is either \(2^k m-1\) or \(2^k m+1\) for a
unique C2 address \((k,m,\pm)\) with \(k\ge2\) and \(m\) odd.
\end{theorem}

This section is purely combinatorial.  Its purpose is to show that the
odd integers can be regrouped by dyadic brackets without loss or multiplicity.
In Lean, the existence and uniqueness statements are formalized as
\[
\begin{gathered}
\Lean{C2.bracket\_bijection\_odd\_ge\_three\_exists},\\
\Lean{C2.bracket\_bijection\_odd\_ge\_three}.
\end{gathered}
\]
The corresponding weight identity is
\[
  \Lean{C2.halving\_law\_odd\_ge\_three}.
\]

\section{The genuine C2 numerator}

The genuine direct lateral operator is
\[
  D_\infty(s)
  =
  \sum_{\substack{n\ {\rm odd}\\ n\ge3}}
    2^{-k_{\mathrm{eff}}(n)} n^{-s}.
\]
The genuine bracket operator is
\[
  B_\infty(s)
  =
  \sum_{k\ge2}\sum_{\substack{m\ {\rm odd}}}
    2^{-k}\left((c-1)^{-s}+(c+1)^{-s}-2c^{-s}\right),
  \qquad c=2^k m.
\]
We define the genuine C2 numerator by
\[
  F(s):=D_\infty(s)-B_\infty(s).
\]

The bracket bijection implies that the lateral terms in \(D_\infty\) and
\(B_\infty\) match exactly.  Hence, in the half-plane where the series are
absolutely convergent,
\[
  D_\infty(s)-B_\infty(s)
  =
  2\sum_{k\ge2}\sum_{\substack{m\ {\rm odd}}}
    2^{-k}(2^k m)^{-s}.
\]
This cancellation is exact.  It is not a numerical observation and does not
depend on a cutoff.

The corresponding Lean declarations are:
\begin{quote}\small
\Lean{C2.directLateralInfinite\_sub\_bracketLateralInfinite\_eq\_central\_of\_one\_lt\_re}\\
\Lean{C2.genuineFInfinite\_eq\_central\_of\_one\_lt\_re}
\end{quote}

\section{Formal setup}

Let \(s = \sigma + it \in \C\).  The critical strip is the region
\[
  0 < \operatorname{Re}(s) < 1,
\]
and the critical line is \(\operatorname{Re}(s)=1/2\).  The off-critical strip
is the portion of the critical strip with \(\operatorname{Re}(s) \ne 1/2\).

\begin{definition}[Off-critical nonvanishing]
For a function \(F : \C \to \C\), off-critical nonvanishing means
\[
  F(s) \ne 0
\]
for every \(s\) in the off-critical strip.
\end{definition}

In the public Lean facade this predicate is exposed as
\[
  \Lean{C2.PeerReview.OffCriticalNonvanishing}.
\]

The official endpoint is not a local replacement for the Riemann hypothesis.
It is the proposition already provided by mathlib:
\[
  \RH .
\]

\section{\texorpdfstring{The fundamental identity \(F=c_0\zeta\)}
  {The fundamental identity F=c0 zeta}}

From the central form of the genuine numerator,
\[
  F(s)
  =
  2\sum_{k\ge2}\sum_{\substack{m\ {\rm odd}}}
    2^{-k}(2^k m)^{-s},
\]
we separate the depth and odd-core variables:
\[
  F(s)
  =
  2\left(\sum_{k\ge2}2^{-k(1+s)}\right)
   \left(\sum_{\substack{m\ {\rm odd}}}m^{-s}\right).
\]
The odd Dirichlet channel is
\[
  \sum_{\substack{m\ {\rm odd}}}m^{-s}
  =
  (1-2^{-s})\Zeta(s),
\]
and the depth sum is
\[
  \sum_{k\ge2}2^{-k(1+s)}
  =
  \frac{2^{-2(1+s)}}{1-2^{-(1+s)}}.
\]
Thus
\[
  F(s)=c_0(s)\Zeta(s),
  \qquad
  c_0(s)=\frac{2^{-2s}(2^s-1)}{2\cdot2^s-1}.
\]

In the Lean source, the identity in the absolute-convergence half-plane is
checked by
\[
  \Lean{C2.genuineFInfinite\_eq\_c0\_mul\_riemannZeta\_of\_one\_lt\_re}.
\]
The public route consumes the corresponding continuation data through
\[
  \Lean{C2.PeerReview.GenuineC2ContinuationData}.
\]

\subsection{Nonvanishing of the normalizing factor}

On the critical line \(s=1/2+it\), writing \(2^s=\sqrt2\,e^{it\log2}\) gives
\[
  c_0(s)=
  \frac{2^{-2s}(2^s-1)}{2\cdot2^s-1}.
\]
Neither \(2^s-1\) nor \(2\cdot2^s-1\) can vanish on that line: their equations
would force a unit complex number to have modulus \(1/\sqrt2\) or
\(1/(2\sqrt2)\).  More generally, in the positive half-plane the public Lean
identity layer uses
\[
  \Lean{C2.c0\_ne\_zero\_of\_re\_pos}.
\]

\subsection{Transfer principle}

The final transfer layer is separate from the construction of \(F\).  It uses
the identity \(F=c_0\Zeta\) and nonvanishing of \(c_0\) to transport
nonvanishing from the C2 numerator to \(\Zeta\).

\begin{theorem}[C2/zeta transfer]
Assume the C2/zeta identity on the off-critical strip and assume that the C2
operator \(F\) is nonvanishing there.  Then \(\Zeta\) is nonvanishing on the
off-critical strip.  Consequently, mathlib's \RH{} follows.
\end{theorem}

The review-facing Lean declarations are:
\begin{quote}\small
\Lean{C2.PeerReview.C2FundamentalIdentityOnRightHalfPlane}\\
\Lean{C2.PeerReview.C2FundamentalIdentityOnOffCriticalStrip}\\
\Lean{C2.PeerReview.ZetaNonvanishing\_of\_C2Nonvanishing}\\
\Lean{C2.PeerReview.RiemannHypothesis\_of\_C2Nonvanishing}
\end{quote}

\section{Critical branch barrier and transversal tilt}

The critical line also appears internally in the C2 branch geometry.  The
quadratic branch mass is a function of \(\sigma=\operatorname{Re}(s)\) alone:
\[
  \|\mathcal W_\infty(s)\|^2
  =
  \frac{2^{1-4\sigma}}{1-2^{-2\sigma}}.
\]
The \(t\)-dependence disappears because
\[
  |2^{-ks}|^2=2^{-2k\sigma}.
\]
Consequently,
\[
  \|\mathcal W_\infty(s)\|^2<1
  \iff
  \sigma>\frac12,
\]
and
\[
  \|\mathcal W_\infty(s)\|^2=1
  \iff
  \sigma=\frac12.
\]
The Lean statements are:
\begin{quote}\small
\Lean{C2.branchNormSq\_closed\_form}\\
\Lean{C2.branchNormSq\_barrier}\\
\Lean{C2.branchNormSqSigmaT\_eq\_one\_on\_critical}
\end{quote}

The transversal displacement from the critical line is written
\[
  s=\frac12+\delta+it.
\]
Then
\[
  n^{-s}=n^{-1/2}n^{-it}n^{-\delta}.
\]
The C2 tilt is the real factor
\[
  \operatorname{Tilt}_\delta(n)=n^{-\delta},
\]
and its centered bracket is
\[
  \Delta^2[\operatorname{Tilt}_\delta](c)
  =
  (c-1)^{-\delta}+(c+1)^{-\delta}-2c^{-\delta}.
\]
At \(\delta=0\), the tilt is constant and the bracket vanishes.  Away from the
critical line the bracket has a definite sign in the strip-relevant range.  In
Lean this is recorded by:
\begin{quote}\small
\Lean{C2.bracket\_tilt\_zero}\\
\Lean{C2.bracket\_tilt\_pos}\\
\Lean{C2.bracket\_tilt\_neg}\\
\Lean{C2.bracket\_tilt\_zero\_iff\_delta\_zero}
\end{quote}

\section{Regional cover of the off-critical strip}

The C2 proof of off-critical nonvanishing is assembled from three regimes:
\[
  \text{near-critical-zero}
  \quad\cup\quad
  \text{middle-region}
  \quad\cup\quad
  \text{edge-region}.
\]

\begin{theorem}[Regional cover assembly]
If the near-critical-zero, middle-region, and edge-region certificates cover
the off-critical strip and each certificate proves nonvanishing of the same C2
operator on its region, then that operator is nonvanishing on the whole
off-critical strip.
\end{theorem}

In Lean this assembly is exposed by:
\[
  \Lean{C2.PeerReview.OffCriticalNonvanishing\_of\_regionalCover}.
\]
The corresponding terminal route uses:
\[
  \Lean{C2.PeerReview.OffCriticalRegionalCover}.
\]

\section{The genuine C2 operator and continuation}

The complete operator used in the final route is the genuine C2 operator,
exposed in the public facade as
\[
  \Lean{C2.PeerReview.GenuineC2Operator}.
\]
The continuation data are packaged by
\[
  \Lean{C2.PeerReview.GenuineC2ContinuationData}.
\]

The role of this layer is to connect the genuine operator to the continued
central odd channel and to provide the identity bridge used by the regional
cover.  The current route obtains near-critical-zero data from continuation via
the internal constructor
\[
  \Lean{C2.GenuineFInfiniteNearAxisData.of\_continuation}.
\]

\section{Near-critical-zero regime}

Near points associated with the critical line, the route uses local punctured
nonvanishing.  This must be formulated for arbitrary multiplicity.  If
\[
  \rho=\frac12+i\gamma
\]
is a critical-line zero of multiplicity \(m_\rho\), then the genuine identity
gives
\[
  \partial_\sigma^{m_\rho}F(\rho)
  =
  c_0(\rho)\,\Zeta^{(m_\rho)}(\rho)\ne0.
\]
Taylor expansion in the transversal direction yields
\[
  F(\rho+\delta)
  =
  \frac{\delta^{m_\rho}}{m_\rho!}
  \partial_\sigma^{m_\rho}F(\rho)
  +
  R_{m_\rho+1}(\delta),
\]
and therefore a local lower bound of the form
\[
  |F(\rho+\delta)|
  \ge
  A_\rho|\delta|^{m_\rho}
  -
  B_\rho(r)|\delta|^{m_\rho+1}.
\]
Hence there is a positive radius \(\delta_\rho^G>0\) such that
\[
  0<|\delta|<\delta_\rho^G
  \quad\Longrightarrow\quad
  F(\rho+\delta)\ne0.
\]

This regime is not an assumption that all zeros of \(\Zeta\) already lie on the
critical line.  It is one component of the regional cover: it supplies
punctured transverse neighborhoods around the critical-line zero data provided
by the continuation package.  Off-critical points not covered by those
neighborhoods are handled by the middle-region certificate and the edge
component of the same cover.

The relevant public data are:
\begin{quote}\small
\Lean{C2.PeerReview.GenuineNearCriticalZeroData}\\
\Lean{C2.PeerReview.GenuineTaylorBoundsFamilyData}\\
\Lean{C2.PeerReview.GenuineLeibnizTaylorBoundsFamilyData}
\end{quote}

\begin{theorem}[Near-critical-zero certificate]
The continuation package for the genuine C2 operator supplies the
near-critical-zero certificate required by the off-critical regional cover.
\end{theorem}

This statement is represented internally by
\[
  \Lean{C2.GenuineFInfiniteNearAxisData.of\_continuation}.
\]

\section{Middle-region resolvent non-cancellation}

The middle-region proof is expressed as a dominance argument.  A main dyadic
contribution is isolated and compared against residual terms coming from tilt,
horizontal, cutoff, tail, and truncation estimates.

The vertical depth ratio is
\[
  q(s)=2^{-(1+s)}.
\]
On the critical line this has the form
\[
  q(s)=2^{-3/2}e^{-it\log2}=re^{i\theta},
  \qquad r=2^{-3/2}.
\]
The full vertical tower is governed by the resolvent
\[
  T_r(\theta)=\frac{1}{1-re^{i\theta}},
\]
and the four-level prefix is
\[
  P_r(\theta)=1+re^{i\theta}+r^2e^{2i\theta}+r^3e^{3i\theta}.
\]
The corresponding sharp lower bounds are
\[
  \inf_\theta |T_r(\theta)|=\frac{1}{1+r},
  \qquad
  \inf_\theta |P_r(\theta)|=(1-r)(1+r^2).
\]
Thus the quartet is not an experimental choice of four terms; it is a natural
finite prefix of the vertical resolvent.

The Lean route records the resolvent and quartet interfaces through:
\begin{quote}\small
\Lean{C2.geom\_resolvent}\\
\Lean{C2.resolvent\_lower\_bound}\\
\Lean{C2.verticalQuartetPrefix}\\
\Lean{C2.verticalQuartetPrefix\_norm\_lower\_bound\_of\_offCriticalStrip}
\end{quote}

\begin{definition}[Dominant four-level block]
The dominant four-level block is the main finite dyadic contribution used as
the lower-bound side of the middle-region non-cancellation argument.
\end{definition}

\begin{definition}[Residual budget]
The residual budget is the collection of upper bounds for all terms not
included in the dominant four-level block.
\end{definition}

\begin{theorem}[Resolvent non-cancellation criterion]
If the dominant four-level block is strictly larger than the residual budget
throughout the middle region, then the C2 operator is nonvanishing throughout
that region.
\end{theorem}

In its finite adjusted form, the criterion has the schematic shape
\[
  \text{main}-\text{defect}-\text{tail}-\text{residual}>0.
\]
Equivalently, for a decomposition
\[
  F_X(s)=Q_{4,X}(s)+\mathcal T_{4,X}(s)+R_X(s),
\]
a sufficient condition is
\[
  |Q_{4,X}(s)|
  >
  |\mathcal T_{4,X}(s)|+|R_X(s)|.
\]
The paper uses the formal name ``resolvent non-cancellation'' for this layer.
Historical informal labels are not part of the published theorem names.

The public facade exposes this layer through declarations such as
\[
\begin{gathered}
\Lean{C2.PeerReview.DominantFourLevelBlockInequality},\\
\Lean{C2.PeerReview.ResidualBudgetDominance},\\
\Lean{C2.PeerReview.ResolventNonCancellationCriterion\_of\_budgetBounds},\\
\Lean{C2.PeerReview.AdjustedResolventNonCancellationCriterion\_of\_residualBudgetBounds}.
\end{gathered}
\]

The current canonical middle-region witness is
\[
  \Lean{C2.C2CanonicalClosedScaledMiddleLocalData},
\]
with the review-facing alias
\[
  \Lean{C2.PeerReview.CanonicalClosedScaledMiddleLocalData}.
\]

\subsection{Bound and witness packages}

The main middle-region certificate families include:
\begin{quote}\small
\Lean{C2ExpandedScalarScaleData}\\
\Lean{C2ExpandedHorizontalLayerBudget}\\
\Lean{C2ExpandedSeedScaledBound}\\
\Lean{C2ExpandedCutoffScaledBound}\\
\Lean{C2ExpandedQuartetDominance}\\
\Lean{C2ExpandedScalarMainInequalities}\\
\Lean{C2ExpandedScalarLocalBulkData}\\
\Lean{C2CanonicalClosedScaledLocalData}\\
\Lean{C2CanonicalClosedScaledResidualBudgetLocalData}\\
\Lean{C2ResolventNonCancellationGenuineCentralLocalData}
\end{quote}
The continued-model middle region used by the public terminal route is named
\[
  \Lean{C2.PeerReview.ContinuedModelTerminalMiddleRegion}.
\]
The full inventory is maintained in
\Lean{docs/BOUNDS\_CERTIFICATES\_WITNESSES.md}.

\section{Cutoff and residual control}

The finite certified operators approximate the genuine operator through an
explicit cutoff.  If \(F_X\) denotes the cutoff model, the residual is
\[
  R_X(s)=F_\infty(s)-F_X(s).
\]
A typical cutoff contribution has the form
\[
  g_X(n)=e^{-n/X}-1,
\]
so that the residual can be expanded and bounded as a genuine analytic budget.
The cutoff is therefore not an unrelated numerical device; it is one of the
quantitative terms in the middle-region certificate.

In the public Lean inventory this layer is represented by cutoff and residual
packages such as:
\begin{quote}\small
\Lean{C2.PeerReview.BalancingSeedExplicitCutoffEstimates}\\
\Lean{C2.PeerReview.BalancingSeedExplicitCutoffOneLtEstimates}\\
\Lean{C2.PeerReview.PointwiseOscillatoryResidualUpper}\\
\Lean{C2.PeerReview.ExponentialPointwiseOscillatoryResidualUpper}
\end{quote}

\section{Gluing and edge-region handling}

The regional-cover abstraction includes an edge-region certificate.  In the
current main route, no nontrivial edge construction is required: the selected
continued model uses the empty edge certificate
\[
  \Lean{C2.C2OddTailContinuedBalancingSeedBulkModelEdgeData.empty}.
\]
This is not an omitted case.  The edge certificate is empty because the selected
near/middle cover already covers the relevant off-critical region in the
terminal route.  The empty edge component is still recorded formally, so the
regional cover has a uniform near/middle/edge interface.

The gluing theorem is the statement that the near-critical-zero region, the
middle region, and the edge region cover the off-critical strip, and that the
same C2 operator is nonvanishing on each piece.  It concludes
\[
  F(s)\ne0
  \qquad
  (0<\operatorname{Re}(s)<1,\ \operatorname{Re}(s)\ne1/2).
\]
The public Lean wrapper for this assembly is
\[
  \Lean{C2.PeerReview.OffCriticalNonvanishing\_of\_regionalCover}.
\]

\section{Terminal certificate and endpoint}

The terminal certificate is the compact package consumed by the final theorem.
Internally it is the structure
\[
  \Lean{C2.RiemannHypothesisTerminalData}.
\]
It records the calibrated cutoff parameters, horizontal budgets, and the
canonical closed/scaled middle local witness.  In the public facade it is named
\[
  \Lean{C2.PeerReview.RiemannHypothesisTerminalCertificate}.
\]

\begin{center}
\scriptsize
\begin{tabular}{>{\raggedright\arraybackslash}p{0.24\textwidth}
                >{\raggedright\arraybackslash}p{0.40\textwidth}
                >{\raggedright\arraybackslash}p{0.26\textwidth}}
\hline
Field or component & Meaning & Lean source \\
\hline
\Lean{coreCutoff} & cutoff schedule for the certified finite model &
\Lean{RiemannHypothesisTerminalData} \\
\Lean{K}, \Lean{M} & calibrated dyadic and truncation parameters &
\Lean{RiemannHypothesisTerminalData} \\
\Lean{horizontalConstant}, \Lean{horizontalScale}, \Lean{horizontalRatio} &
horizontal-budget functions used in the canonical closed/scaled middle route &
\Lean{RiemannHypothesisTerminalData} \\
\Lean{middle.near} & canonical near-axis data for the continued C2 model &
\Lean{C2CanonicalClosedScaledMiddleLocalData} \\
\Lean{middle.edge} & edge component; empty in the selected terminal route &
\Lean{C2CanonicalClosedScaledMiddleLocalData} \\
\Lean{middle.middle\_local} & pointwise middle-region local witness proving the
canonical closed/scaled budget at each covered point &
\Lean{C2CanonicalClosedScaledMiddleLocalData} \\
\hline
\end{tabular}
\end{center}

\begin{theorem}[Terminal endpoint]
Given a terminal C2 certificate, the official mathlib proposition \RH{} follows.
\end{theorem}

The Lean theorem is:
\[
  \Lean{C2.PeerReview.RiemannHypothesis\_of\_terminalCertificate}.
\]
Its proof is a wrapper over the internal declaration
\[
  \Lean{C2.mathlibRiemannHypothesis\_of\_terminalData}.
\]
The public facade also exposes the canonical constructor from the continued
model near-axis data and middle-local data,
\[
  \Lean{C2.PeerReview.TerminalCertificate\_of\_continuedModelMiddleLocal},
\]
and the corresponding endpoint
\[
  \Lean{C2.PeerReview.RiemannHypothesis\_of\_continuedModelMiddleLocal}.
\]
The public facade also records the reduced pointwise target for the same
continued-model middle region:
\begin{quote}\small
\Lean{C2.PeerReview.TerminalCertificate\_of\_continuedModelCanonicalClosedScaledMiddleResidualPointwiseBounds}\\
\Lean{C2.PeerReview.RiemannHypothesis\_of\_continuedModelCanonicalClosedScaledMiddleResidualPointwiseBounds}.
\end{quote}
The continuation-based pair
\Lean{C2.PeerReview.TerminalCertificate\_of\_continuationAndMiddleLocal} and
\Lean{C2.PeerReview.RiemannHypothesis\_of\_continuationAndMiddleLocal} is still
available as an audit variant.  As of this working revision, these are explicit
route-package endpoints rather than a zero-argument theorem obtained by applying
a public \Lean{terminalCertificate} constant.

\section{Lean implementation}

The paper-facing Lean entry point is:
\begin{quote}\small
\begin{verbatim}
import LeanC2.PeerReview
\end{verbatim}
\end{quote}
This facade imports the concrete route and exposes stable names in namespace
\[
  \Lean{C2.PeerReview}.
\]

The formerly monolithic concrete bulk implementation is now split under:
\[
  \Lean{LeanC2/Analytic/GenuineBulkConcrete/}.
\]
The stable import
\[
  \Lean{LeanC2.Analytic.GenuineBulkConcrete}
\]
remains a facade.  The smallest staged module containing the canonical terminal
certificate route is
\[
  \Lean{LeanC2.Analytic.GenuineBulkConcrete.Terminal}.
\]

\subsection{Paper-to-Lean map}

\begin{center}
\scriptsize
\begin{tabular}{>{\raggedright\arraybackslash}p{0.35\textwidth}
                >{\raggedright\arraybackslash}p{0.55\textwidth}}
\hline
Paper-level statement & Lean declaration \\
\hline
Off-critical nonvanishing implies RH &
\Lean{C2.PeerReview.RiemannHypothesis\_of\_offCriticalNonvanishing} \\
C2/zeta transfer to zeta nonvanishing &
\Lean{C2.PeerReview.ZetaNonvanishing\_of\_C2Nonvanishing} \\
C2/zeta transfer to RH &
\Lean{C2.PeerReview.RiemannHypothesis\_of\_C2Nonvanishing} \\
Regional cover assembly &
\Lean{C2.PeerReview.OffCriticalNonvanishing\_of\_regionalCover} \\
Middle-region budget criterion &
\Lean{C2.PeerReview.ResolventNonCancellationCriterion\_of\_budgetBounds} \\
Adjusted residual-budget criterion &
\Lean{C2.PeerReview.AdjustedResolventNonCancellationCriterion\_of\_residualBudgetBounds} \\
Terminal endpoint &
\Lean{C2.PeerReview.RiemannHypothesis\_of\_terminalCertificate} \\
Canonical terminal assembly &
\Lean{C2.PeerReview.RiemannHypothesis\_of\_continuedModelMiddleLocal} \\
Residual terminal assembly &
\Lean{C2.PeerReview.TerminalCertificate\_of\_continuedModelCanonicalClosedScaledMiddleResidualPointwiseBounds} \\
Continued-model residual middle endpoint &
\Lean{C2.PeerReview.RiemannHypothesis\_of\_continuedModelCanonicalClosedScaledMiddleResidualPointwiseBounds} \\
\hline
\end{tabular}
\end{center}

\section{Reproducibility}

The certified Lean snapshot currently referenced by this draft is release
v1.1.0:
\begin{center}
  \url{https://github.com/thiagomassensini/dyadic_geometry_zeta_fuction/releases/tag/v1.1.0}.
\end{center}
The Zenodo archive for this snapshot is:
\begin{center}
  \url{https://doi.org/10.5281/zenodo.20401742}.
\end{center}
The paper source should be archived under a fresh tag when the draft is frozen
for review.

The Lean verification command is:
\begin{verbatim}
lake build LeanC2.Analytic.GenuineBulkConcrete LeanC2.PeerReview LeanC2
\end{verbatim}
The command is also run by the GitHub Actions workflow
\Lean{Lean C2 CI}.

\section{Discussion}

The route is intentionally modular.  The C2/zeta transfer, the regional cover,
the near-critical-zero package, the middle-region non-cancellation mechanism,
and the terminal certificate can be audited separately.  This modularity is
useful both mathematically and formally: the paper can state conceptual
theorems, while the Lean development records the exact certificate objects and
bound packages consumed by those theorems.

For external review, the normative maps are:
\[
\begin{array}{ll}
\Lean{docs/MAIN\_ROUTE\_MAP.md},&
\Lean{docs/THEOREM\_MAP\_REVIEW.md},\\
\Lean{docs/BOUNDS\_CERTIFICATES\_WITNESSES.md},&
\Lean{docs/LEAN\_MODULE\_LAYOUT.md},\\
\Lean{docs/REPRODUCIBILITY.md}.&
\end{array}
\]

\appendix

\section{Non-terminal residual route}

The fully explicit finite exact-zeta residual route is kept in the Lean source
as a documented obstruction rather than as the current terminal target.  The
formal statements are:
\begin{quote}\small
\Lean{c2ExpandedQuartetResidualMargin\_lt\_scaledVerticalDepthTail\_of\_offCriticalStrip}\\
\Lean{c2AnalyticBulkAllowance\_sub\_reserve\_lt\_scaledVerticalDepthTail\_of\_offCriticalStrip}\\
\Lean{not\_c2CanonicalClosedScaledResidualFiniteExactZetaUpper\_lt\_analyticResidual\_of\_offCriticalStrip}
\end{quote}
The terminal route therefore uses sharper middle-region witnesses rather than
forcing this coarse residual inequality.

\section{Naming policy}

The paper avoids informal discovery labels.  The middle-region mechanism is
called a resolvent non-cancellation mechanism, the main finite contribution is
called the dominant four-level block, and the correction data are called
calibrated residual budgets or calibrated residual seeds.  The public naming
policy is recorded in \Lean{docs/FORMAL\_NAMING.md}.

\section{Audit checks and hidden assumptions}

The public Lean tree should be checked for unclosed placeholders with:
\begin{quote}\small
\begin{verbatim}
rg "\bsorry\b|\badmit\b|^\s*axiom\b|^\s*constant\b" LeanC2 LeanC2.lean
\end{verbatim}
\end{quote}
On the current v1.1.0-based draft this command returns no matches in
\Lean{LeanC2}.  This check is separate from the certificate boundary: the
terminal theorem is still a theorem over the explicit
\Lean{RiemannHypothesisTerminalData} interface unless a closed certificate term
is supplied and named.

\begin{thebibliography}{9}

\bibitem{repo}
Thiago F. M. Massensini Silva.
\emph{Dyadic Geometry of the Zeta Function -- Formal Lean Verification}.
GitHub repository, release v1.1.0.
\repo.

\bibitem{zenodo}
Thiago F. M. Massensini Silva.
\emph{Dyadic Geometry of the Zeta Function -- Formal Lean Verification}.
Zenodo archive, 2026.
\url{https://doi.org/10.5281/zenodo.20401742}.

\bibitem{lean}
Lean FRO.
\emph{The Lean theorem prover}.
\url{https://lean-lang.org/}.

\bibitem{mathlib}
The mathlib community.
\emph{The Lean mathematical library}.
\url{https://leanprover-community.github.io/}.

\end{thebibliography}

\end{document}
